Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
ciao

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plans represented as linear, time invariant models. 
Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.

\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
Quantisation; 
Fixed-point arithmetics; 
CEGIS; 
safety requirements. 
}
\end{abstract}
